Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre

### 2024-10-21 manuscript/manuscript.Rmd
Rephrasing sample extraction to be more clear

## Metabolite sample extraction
Extraction followed a modified Bligh & Dyer approach as detailed in @Boysen2018. Briefly, filters were randomized and added to PTFE centrifuge tubes with a 1:1 mix of 100 µm and 400 µm silica beads, approximately 2 mL -20 °C Optima-grade dichloromethane, and approximately 3 mL -20 °C 1:1 methanol/water solution (both also Optima-grade). Isotope labeled extraction standards were also added during this step (Supplemental Table 1). The samples were then bead-beaten three times, followed by triplicate extraction of the aqueous layer and addition with fresh methanol/water mixture with additional bead-beatings in between. Samples were then dried down under ultrapure nitrogen gas and warmed using a Fisher-Scientific Reacti-Therm module. Dried aqueous fractions were reconstituted in 380 µL Optima-grade water and amended with 20 µL isotope-labeled injection standards (Supplemental Table 1) to measure the variability introduced by chromatography and ionization. The reconstituted fraction was syringe-filtered into precombusted glass inserts in HPLC vials to remove any potential clogging material. Samples were then additionally diluted 1:1 with Optima-grade water to prevent overloading on the column and reduce salt effects.

>>>>

## Metabolite sample extraction
Extraction followed a modified Bligh & Dyer approach as detailed in @Boysen2018. Briefly, filters were randomized and added to PTFE centrifuge tubes with a 1:1 mix of 100 µm and 400 µm silica beads, approximately 2 mL -20 °C Optima-grade dichloromethane, and approximately 3 mL -20 °C 1:1 methanol/water solution (both also Optima-grade). Isotope labeled extraction standards were also added during this step (Supplemental Table 1). The samples were then bead-beaten three times, followed by triplicate extraction of the aqueous layer into a separate vial after spontaneous separation and replacement with fresh methanol/water mixture using a glass Pasteur pipette with additional bead-beatings in between. The aqueous fraction was then dried down under ultrapure nitrogen gas and warmed using a Fisher-Scientific Reacti-Therm module. Dry samples were reconstituted in 380 µL Optima-grade water and amended with 20 µL isotope-labeled injection standards (Supplemental Table 1) to measure the variability introduced by chromatography and ionization. The reconstituted fraction was syringe-filtered into precombusted glass inserts in HPLC vials to remove any potential clogging material. Samples were then additionally diluted 1:1 with Optima-grade water to prevent overloading on the column and to reduce salt effects.
